%-------------------------
% Rover Resume - Fancy Template
% Link: https://github.com/subidit/rover-resume
%------------------------

\documentclass[11pt]{article}

\documentclass{article}
\usepackage[utf8]{inputenc}

% Use these two lines for uppercase X:
\usepackage{amssymb}
\DeclareUnicodeCharacter{1D54F}{$\mathbb{X}$}

\usepackage[T1]{fontenc}
\usepackage{inter} % https://tug.org/FontCatalogue/
\renewcommand*\familydefault{\sfdefault}

\usepackage{geometry}
\geometry{
a4paper,
top=1.8cm,
bottom=1in,
left=2.5cm,
right=2.5cm
}

\setcounter{secnumdepth}{0} % remove section numbering
\pdfgentounicode=1 % make ATS friendly

\usepackage{enumitem}
\setlist[itemize]{
    noitemsep,
    left=0pt..1.5em
}
\setlist[description]{itemsep=0pt}
\setlist[enumerate]{align=left}

\usepackage[dvipsnames]{xcolor}
% \usepackage[dvipsnames, svgnames, x11names]{xcolor} 
% \usepackage[dvipsnames]{xcolor} % xcolor.pdf Sec.4 Colors by Name
\colorlet{icnclr}{gray}
% \colorlet [⟨type⟩]{⟨name⟩}[⟨num model⟩]{⟨color ⟩}
% \definecolor[⟨type⟩]{⟨name⟩}{⟨model-list⟩}{⟨spec-list⟩}


\usepackage{titlesec}
% \titlespacing{command}{left spacing}{before spacing}{after spacing}[right]
% \titlespacing{\section}{0pt}{*3}{*1}
\titlespacing{\subsection}{0pt}{*0}{*0}
\titlespacing{\subsubsection}{0pt}{*0}{*0}
% \titleformat{<command>}[<shape>]{<format>}{<label>}{<sec>}{<before-code>}[<after-code>]  
\titleformat{\section}{\color{Sepia}\large\fontseries{black}\selectfont\uppercase}{}{}{\ruleafter}[\global\RemVStrue]
\titleformat{\subsection}{\large\fontseries{semibold}\selectfont}{}{}{\rvs}
\titleformat{\subsubsection}{\large\fontseries{medium}\selectfont}{}{}{}

\usepackage{xhfill} 
\newcommand\ruleafter[1]{#1~\xrfill[.5ex]{1pt}[gray]} % add rule after title in .5 x-height 

\newif\ifRemVS % remove vspace between \section & \subsection
\newcommand{\rvs}{
    \ifRemVS
        \vspace{-1.5ex}
    \fi
    \global\RemVSfalse
}


\usepackage{fontawesome5}

\usepackage[bookmarks=false]{hyperref} % [imp!]
\hypersetup{ % https://en.wikibooks.org/wiki/LaTeX/Hyperlinks
    colorlinks=true,
    urlcolor=Sepia,
    pdftitle={My Resume},
}

\usepackage[page]{totalcount}
\usepackage{fancyhdr}
\pagestyle{fancy}
\renewcommand{\headrulewidth}{0pt}	
\fancyhf{}							
\cfoot{\color{darkgray} Rover R\'esum\'e -- Page \thepage{} of \totalpages}


\begin{document}

%== HEADER ==%
\begin{center}
    {\fontsize{36}{36}\selectfont\interthin ADARSH\interheavy KUMAR} \\ \bigskip
    {\faEnvelope[regular]} \href{mailto:adarshkumar20012704@gmail.com}{gmail} $|$ 
    {\faIcon{mobile-alt}} \href{tel:9581420398}{9581420398} $|$
    {\faGithub} \href{https://github.com/adarshkumar714}{adarshkumar714} $|$
    {\faLinkedinIn} \href{https://www.linkedin.com/in/adarsh-kumar-123a34231/}{Adarsh Kumar} $|$
    {$X$} \href{https://twitter.com/akn714/}{akn714}
\end{center}

\section{Education}
%==============

\subsection{Rajkiya Engineering College $|$ {\normalfont\textit{Mainpuri, Uttar Pradesh}} \hfill 2022 -- 2026}
{B.Tech. - Major in Computer Science and Engineering \hfill CGPA: 8}
% \begin{itemize}
%     \item B.Tech. - Major in Computer Science and Engineering 
%     \item Cumulative GPA: 8
% \end{itemize}

\subsection{Sarvajanik Vidyalaya $|$ {\normalfont\textit{Daman, Daman & Diu}} \hfill 2019 -- 2021}
{11th - 12th Standard \hfill Percentage: 80%}
% \begin{itemize}
%     \item 11th - 12th Standard
%     \item Percentage: 80%
% \end{itemize}

\subsection{Coast Guard Public School $|$ {\normalfont\textit{Daman, Daman & Diu}} \hfill 2018 -- 2019}
{10th Standard \hfill Percentage: 71%}
% \begin{itemize}
%     \item 10th Standard
%     \item Percentage: 71%
% \end{itemize}

\subsection{KVS - Kendriya Vidyalaya Sangathan \hfill 2010 -- 2018}
{1st - 9th Standard \hfill Percentage: 85%}
% \begin{itemize}
%     \item 1st - 9th Standard
% \end{itemize}

    % \resumeEduheading
    %   {KVS - Kendriya Vidyalaya Sangathan}{Visakhapatnam, Andhra Pradesh}
    %   {Secondary}
    %   {2010 -- 2018}
    %   {}


\section{About}
\begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     I'm Adarsh Kumar, a B.Tech student majoring in Computer Science and Engineering. Proficient in JavaScript, Java, and Python, my passion lies in both frontend and backend projects, showcasing a diverse skill set in full-stack development.

    In my journey, I've explored a range of technologies, fostering a keen interest in computer science intricacies. I'm dedicated to continuous learning and naturally inclined to explore hacking, alongside a fondness for the Linux operating system.
    
    My future aspirations involve building a career as a software developer, focusing on networking and web development. I aim to contribute meaningfully to projects, stay updated on emerging technologies, and actively engage in the evolving tech industry.
    }}\\
 \end{itemize}


\section{Skills}
%===============
\begin{description}
        \item \textbf{Languages:} \newline
        Python, Javascript, Java, C/C++, Bash/Shell Scripting, HTML/CSS.
        \item \textbf{Libraries / Frameworks / Tools:} \newline
        Node.js, Flask, Langchain, Socket.IO, BeautifulSoup, Express.js, React.js, Mongoose, OpenAI, Pinecone, Telegram SDK, Discord SDK. Git/Github, Linux, Tmux.
        \item \textbf{Experience in:} \newline
        Object Oriented Programming Systems, Data Structures and Algorithms, TryHackMe, Generative AI, Web Development, CLI Development, Open Source Development.
        \item \textbf{Achievements:} \newline
        Certificate and 5-star rated in Python, Problem Solving, and Java on HackerRank. 1600 rating on CodeChef. 1000 rating on Codeforces. College best coder award.
\end{description}


\section{Relevant Courses}
\begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
    Data Structures and Algorithms, Computer Networks, Discrete Mathematical Structures, Command Line Interfaces, Computer Organization and Architecture, Networking, Cybersecurity, Engineering physics, Engineering maths 1, 2 & 3, Fundamentals of electrical engineering, Fundamentals of electronics engineering, programming of problem solving, fundamentals of mechanical engineering, soft skills, etc.
    }}\\
 \end{itemize}


\section{Projects}
%=================

\subsection{V-Doc {\normalfont $|$ \href{https://github.com/adarshkumar714/V-Doc}{\textit{GitHub Link}}} \hfill Jul 2023 - Oct 2023}
\begin{itemize}
    \item Languages / Tools: Python, JavaScript. Flask, Langchain, Pinecone, React.js.
    \item An AI assistant leveraging medication data to suggest appropriate treatments for various diseases and injuries, balancing efficacy with safety in its recommendations.
\end{itemize}

\subsection{cOLX {\normalfont $|$ \href{https://github.com/adarshkumar714/colx}{\textit{GitHub Link}}} \hfill Jul 2023 - Oct 2023}
\begin{itemize}
    \item Languages / Tools: JavaScript. Node.js, Express.js, React.js.
    \item College OLX, A versatile college platform akin to OLX, enabling trade of second-hand items, lost and found posts, and maintenance requests.
\end{itemize}

\subsection{Discord AI Bot {\normalfont $|$ \href{https://github.com/adarshkumar714/Discord-AI-Bot}{\textit{GitHub Link}}} \hfill Jul 2023}
\begin{itemize}
    \item Language / Tools: Python. Pinecone, Discord SDK, Langchain.
    \item A custom-trained Discord AI bot, seamlessly integrating ChatGPT with RAG, tailored to your data for enriched, contextually relevant interactions and responses.
\end{itemize}

\subsection{Chat Room {\normalfont $|$ \href{https://github.com/adarshkumar714/chat-room}{\textit{GitHub Link}}} \hfill Mar 2023 - Jun 2023}
\begin{itemize}
    \item Languages / Tools: Node.js, JavaScript. Express.js, Socket.io.
    \item A dynamic real-time chat app for instant messaging and seamless communication.
\end{itemize}

\subsection{YouTube Ad Skipper {\normalfont $|$ \href{https://github.com/adarshkumar714/YT-Ad-Skipper}{\textit{GitHub Link}}} \hfill Apr 2023}
\begin{itemize}
    \item Languages / Tools: HTML, CSS, JavaScript. Chrome Dev tools.
    \item A Chrome extension designed to effectively bypass YouTube ads, enhancing your video-watching experience without interruptions.
\end{itemize}

\subsection{Trash N Treasure {\normalfont $|$ \href{https://github.com/adarshkumar714/YT-Ad-Skipper}{\textit{GitHub Link}}} \hfill Jan 2024}
\begin{itemize}
    \item Languages / Tools: Node.js, JavaScript. Express.js, Socket.io, Nodemailer, MongoDB.
    \item A web portal bridging communities and recycling industries, facilitating efficient waste management and promoting environmental sustainability.
\end{itemize}

\subsection{TelegramGPT {\normalfont $|$ \href{https://github.com/adarshkumar714/TelegramGPT}{\textit{GitHub Link}}} \hfill Oct 2024 - Nov 2023}
\begin{itemize}
    \item Language / Tools: Python. OpenAI SDK, Telegram SDK, Langchain, Pinecone.
    \item An AI assistant for Telegram, utilizing the Retrieval-Augmented Generation (RAG) model, trained on custom data for enhanced, context-aware responses.
\end{itemize}

\subsection{Student Dashboard {\normalfont $|$ \href{https://github.com/adarshkumar714/Student-Dashboard}{\textit{GitHub Link}}} \hfill Oct 2024 - Present}
\begin{itemize}
    \item Languages / Tools: Node.js, HTML, CSS, JavaScript. Express.js, Mongoose, MongoDB, Nodemailer.
    \item A web application featuring an interactive student dashboard, designed for engaging and streamlined access to educational resources and tools.
\end{itemize}


\section{Interests}
\begin{description}
    \item \textbf{Programming:} Proficient in JavaScript, Java, and Python.
    \item \textbf{SaaS Development:} Challenges in both frontend and backend development.
    \item \textbf{Computer Science:} Intricate concepts, especially in networking and web development.
    \item \textbf{Hacking / Playing CTFs:} Exploring and applying cybersecurity principles.
    \item \textbf{Continuous Learning:} Staying updated on emerging technologies.
    \item \textbf{Linux Enthusiast:} Appreciation for the Linux operating system.
\end{description}



\end{document}
